\title{PostgreSQL\textsuperscript{\textregistered} Community Exhibitions}
\subtitle{}
\author[Mark Wong]{Mark Wong\\PostgreSQL Major Contributor\\markwkm@postgresql.org\\EDB Software Development Engineer\\mark.wong@enterprisedb.com}
\institute[PGConf.dev 2025]{PGConf.dev 2025 Montreal, Quebec}
\date{May 2025}

\begin{document}

\setbeamercolor{background canvas}{bg=pgbaseblue}
\frame{\titlepage}

\setbeamertemplate{footline}[postgres body]

\frame
{
  \frametitle{Outline}

  \begin{itemize}
    \item What is this about?
    \item Why do we do it?
    \item What does it take?
    \item How do I get involved?
  \end{itemize}
}

\frame
{
  \frametitle{What is this about?}

  The PostgreSQL\textsuperscript{\textregistered} community may be exhibitors
  at various conferences with:

  \begin{columns}
    \begin{column}{.5\textwidth}
      \begin{itemize}
        \item Banner system
        \item Table cover
        \item SWAG (more later)
      \end{itemize}
    \end{column}
    \begin{column}{.5\textwidth}
      \begin{itemize}
        \item Fliers
          \begin{itemize}
            \item Introduction to PostgreSQL\textsuperscript{\textregistered}
            \item What's new in PostgreSQL\textsuperscript{\textregistered}
            \item Find a PostgreSQL\textsuperscript{\textregistered} MeetUp
            \item Upcoming PostgreSQL\textsuperscript{\textregistered} Events
            \item Diversity information
          \end{itemize}
      \end{itemize}
    \end{column}
  \end{columns}
}

\frame
{
  \frametitle{Events}

  \begin{columns}
    \begin{column}{.33\textwidth}
      \begin{itemize}
        \item SREcon NA
        \item PyCon
        \item RustConf
        \item All Things Open
        \item OSCON
        \item DevOps Day
        \item Ohio LinuxFest
      \end{itemize}
    \end{column}
    \begin{column}{.33\textwidth}
      \begin{itemize}
        \item FOSDEM
        \item SCaLE
        \item DjangoCon
        \item LinuxFest NorthWest
        \item Percona Live
        \item SouthEast LinuxFest
        \item SeaGL
      \end{itemize}
    \end{column}
    \begin{column}{.33\textwidth}
      \begin{itemize}
        \item FOSSY
        \item DevNexus
        \item PASS Data Community Summit
        \item RailsConf
        \item LISA
        \item FOSS4G NA
      \end{itemize}
    \end{column}
  \end{columns}
}

\frame
{
  \frametitle{Why do we do it?}

  \begin{itemize}
    \item Show PostgreSQL is alive and well
    \item Network with individuals
    \item Opportunities for others to engage with active community members
    \item Give away SWAG!
  \end{itemize}
}

\frame
{
  \frametitle{Stuff We All Get}

  Not always available but things that have been given away:

  \begin{columns}
    \begin{column}{.33\textwidth}
      \begin{itemize}
        \item Stickers
        \item Mugs
        \item Temporary Tatoos
      \end{itemize}
    \end{column}
    \begin{column}{.33\textwidth}
      \begin{itemize}
        \item Baseball caps
        \item Enameled pins
      \end{itemize}
    \end{column}
  \end{columns}
}

\frame
{
  \frametitle{What does it take?}

  \begin{itemize}
    \item Engaging with event organizers
    \item Recruiting volunteers
    \item Budgeting travel, shipping, printing, and event fees
    \item Getting volunteer registered
    \item Preparing volunteers for duty
    \item Shipping booths kit to the event
    \item Shipping booths kit back from the event
    \item Reimbursing volunteer travel expenses
  \end{itemize}
}

\frame
{
  \frametitle{How is it funded?}

  No single best way:
  \begin{itemize}
    \item PostgreSQL\textsuperscript{\textregistered} Funds Groups
    \item PGEUi
    \item PgUS
  \end{itemize}
}

\frame
{
  \frametitle{How do I get involved?}

  No single best way:
  \begin{itemize}
    \item Email: PgUS contact@postgresql.us
    \item Social Media: PGEU, PgUS, etc.
  \end{itemize}
}

\frame
{
  \begin{center}
    \Huge Thank you!
  \end{center}

  \note[item]{This is a note.}
}

\end{document}
